COG-ED Manuscript

### 2022-01-06 06_Paper/COG-ED/Manuscript.Rmd
finished adding BFs & changed apa_print functions

A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.

@@

      h1a_data <- pipelines_data[["AARN"]][pipelines_data[["AARN"]]$level != 1, ]
      h1a_data$level <- as.factor(h1a_data$level)

@@

      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)

  hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)

@@

### Associations of subjective and objective task load measures

Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).

@@

      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)

  hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)

@@

However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not different between 2- and 4-back or 3- and 4-back.
Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.

@@

      hypothesis1c_emm <- emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
      hypothesis1c_mental_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
      hypothesis1c_physical_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
      hypothesis1c_time_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
      hypothesis1c_performance_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_effort_rmanova$aov, specs = "level")
      hypothesis1c_effort_contrasts <- pairs(hypothesis1c_emm)

      hypothesis1c_emm <- emmeans(object = hypothesis1c_frustration_rmanova$aov, specs = "level")
      hypothesis1c_frustration_contrasts <- pairs(hypothesis1c_emm)

@@

  hypothesis1c_mental_BF <- anovaBF(formula = mental ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_physical_BF <- anovaBF(formula = physical ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_time_BF <- anovaBF(formula = time ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_performance_BF <- anovaBF(formula = performance ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_effort_BF <- anovaBF(formula = effort ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_frustration_BF <- anovaBF(formula = frustration ~ level, data = h1c_data, progress = FALSE)

@@

Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
Overall, these ratings showed that the increase in task load was being perceived as such.

@@

  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)

  hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)

@@

### Changes in subjective values depending on n-back level

The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
SVs were higher for 1- than 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
Importantly, the lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
This can be considered preliminary proof-of-concept, as this behavioural pattern can only emerge in the CERED paradigm, but not in the original COG-ED paradigm.

@@

  replication_table <-
    kbl(h2b_result.table,
    caption = "Effects of n-back load level on subjective value controlled 
    for task performance (d’ and reaction time), correct and postcorrect trials.",
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote

@@

### Changes in subjective values depend reliably on n-back level

N-back level is a reliable predictor of subjective value (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (signal detection d’ and reaction time) as well as correct and post-correct answers. 
The results of the multilevel model are detailed in Table X. 
`r replication_table`
`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).
However, NFC has no statistically significant effect on subjective value (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
The simple slopes analysis revealed a significant slope of n-back level for three different expressions of NFC (Table X, Figure X).
`r h2b_ss.table`
`r h2b_ss.plot`
The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC. The Johnson-Neyman interval is [`r h2b_jn.int`].
Consequently, the slope of n-back level is not significant for individuals with very low NFC values.    
`r h2b_jn.plot`

@@

@@

>>>>

A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 53 participants, assuming $f=0.20$, $\alpha=.05$, and $\beta=.95$.

@@

      h1a_data <- pipelines_data[["AARN"]][pipelines_data[["AARN"]]$level != 1, ]
      h1a_data <- unique(h1a_data[ ,c("subject","level","dprime")])
      h1a_data$level <- as.factor(h1a_data$level)

@@

      hypothesis1a_contrasts <- as.data.frame(pairs(hypothesis1a_emm))

  hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
  hypothesis1a_contrasts$BF10 <- c(extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf)

@@

We collected data from $N = 16$ participants,
One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 15 complete data sets.
Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).

@@

      hypothesis1b_contrasts <- as.data.frame(pairs(hypothesis1b_emm))

  hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)
  hypothesis1b_contrasts$BF10 <- c(extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 3], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf)

@@

However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level"))[1]`), but not different between 2- and 4-back or 3- and 4-back.
Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.

@@

      hypothesis1c_emm <- emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
      hypothesis1c_mental_contrasts <- as.data.frame(pairs(hypothesis1c_emm))

      hypothesis1c_emm <- emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
      hypothesis1c_physical_contrasts <- as.data.frame(pairs(hypothesis1c_emm))

      hypothesis1c_emm <- emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
      hypothesis1c_time_contrasts <- as.data.frame(pairs(hypothesis1c_emm))

      hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
      hypothesis1c_performance_contrasts <- as.data.frame(pairs(hypothesis1c_emm))

      hypothesis1c_emm <- emmeans(object = hypothesis1c_effort_rmanova$aov, specs = "level")
      hypothesis1c_effort_contrasts <- as.data.frame(pairs(hypothesis1c_emm))

      hypothesis1c_emm <- emmeans(object = hypothesis1c_frustration_rmanova$aov, specs = "level")
      hypothesis1c_frustration_contrasts <- as.data.frame(pairs(hypothesis1c_emm))

@@

  hypothesis1c_mental_BF <- anovaBF(formula = mental ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_mental_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 3], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf)
  hypothesis1c_physical_BF <- anovaBF(formula = physical ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_physical_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf)
  hypothesis1c_time_BF <- anovaBF(formula = time ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_time_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 3], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf)
  hypothesis1c_performance_BF <- anovaBF(formula = performance ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_performance_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 3], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf)
  hypothesis1c_effort_BF <- anovaBF(formula = effort ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_effort_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf)
  hypothesis1c_frustration_BF <- anovaBF(formula = frustration ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_frustration_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 3], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf)

@@

Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X3`, and `r apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X4`, and `r `apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X4`, respectively).
Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
Overall, these ratings showed that the increase in task load was being perceived as such.

@@

  hypothesis2a_contrasts <- as.data.frame(pairs(hypothesis2a_emm))

  hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
  hypothesis2a_contrasts$BF10 <- c(extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf)

@@

The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
SVs were higher for 1- than 3-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X3`), for 1- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X2_X4`).
Importantly, the lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
This can be considered preliminary proof-of-concept, as this behavioural pattern can only emerge in the CERED paradigm, but not in the original COG-ED paradigm.

@@

  table_1 <-
    kbl(h2b_result.table,
    caption = "Effects of n-back load level on subjective value controlled 
    for task performance (d’ and reaction time), correct and postcorrect trials.",
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote

@@

The MLM revealed that n-back level was a reliable predictor of SV (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers. 
The results of the MLM are detailed in Table 1. 
`r table_1`
Differences between subjects could explain `r round((icc_h2b*100), digits = 0)` % of the total variance in SVs ($ICC =$ `r round(icc_h2b, digits = 2)`).
However, NFC had no statistically significant effect on SVs (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
The simple slopes analysis revealed a significant difference in slope of n-back level for three different expressions of NFC (Table 2, Figure 2).
`r h2b_ss.table`
`r h2b_ss.plot`
The Johnson-Neyman plot (Figure 2) visualizes the significance of the slope of n-back level at different values of NFC.
The Johnson-Neyman interval is [`r h2b_jn.int`].
Consequently, the slope of n-back level was not significant for individuals with very low NFC values.    
`r h2b_jn.plot`

@@

  hypothesis3a_BF <- regressionBF(formula = nfc ~ axauc, data = h3_data, progress = FALSE)

@@

  hypothesis3b_BF <- regressionBF(formula = nfc ~ axauc + auc_ntlx, data = h3_data, progress = FALSE)
